Add Amicus Measures

### 2022-05-10 data-cleaning/00-scrape-amicus-text.Rmd
add missing amicus + lit briefs

# run the function for Abortion and Sex Discrim folders
amicus_file_ids <- all_file_names(case_folders)

@@

@@

@@

```{r}
box_write(amicus_txt,
          file_name = "raw-amicus-brief-text.csv",
          dir_id = '145990409196')
```

>>>>

# run the function for Abortion folders
amicus_file_ids <- all_file_names(case_folders)

@@

If only need to scrape briefs ad hoc, filter now

```{r}
amicus_file_ids <- amicus_file_ids %>% filter(id == "861822172835")
```

Scrape text

@@

If adding in briefs, run below

```{r}
full <- box_read("863216279471")
full <- full %>% rbind(amicus_txt) %>% arrange(case)
```

@@

```{r}
box_write(full,
          file_name = "raw-amicus-brief-text.csv",
          dir_id = '145990409196')
```

### 2022-05-10 data-cleaning/00b-scrape-litigant-text.Rmd
add missing amicus + lit briefs

Set working directory to  files folder

```{r}
box_setwd("6932017842")
```

@@

# filter for only briefs that need to be re-pulled
litigant_file_ids <- litigant_file_ids %>% 
  filter(id %in% c("955405762992", "955404304453", "955405038378", "955401734984", "56699188926", "56701967150","56698341318"))
```

@@

```{r}
litigant_all <- box_read("955333134918") %>%
  filter(!(brief %in% c("Bellotti v Baird (1976). Brief for Appellees (feminist).docx",
                       "Colautti v. Franklin. Brief for Respondent (Feminist) - (labeled Beal v Franklin).pdf",
                       "Doe v. Bolton Brief for Petitioners (Feminist).pdf",
                       "Doe v. Bolton Brief for Respondents.pdf",
                       "H.L. v Matheson. Brief for Appellant (feminist).docx",
                       "United States v Vuitch. Brief for Appellant %28United States%29.docx",
                       "United States v. Vuitch. Brief for Respondent (Feminist).pdf"))) %>% 
  rbind(litigant_txt)
```

@@

```{r}
box_write(litigant_txt,
          file_name = "raw-litigant-brief-text.csv",
          dir_id = '162588272045')
```

>>>>

Set working directory to litigant/amicus files folder

```{r}
box_setwd("146066009084")
```

@@

# filter for only briefs that need to be re-pulled
litigant_file_ids <- litigant_file_ids %>% 
  #filter(id %in% c("955405762992", "955404304453", "955405038378", "955401734984", "56699188926", "56701967150","56698341318"))
  filter(id == "861821337076")
```

@@

```{r}
litigant_all <- box_read("955333134918") %>%
  #filter(!(brief %in% c("Bellotti v Baird (1976). Brief for Appellees (feminist).docx",
  #                     "Colautti v. Franklin. Brief for Respondent (Feminist) - (labeled Beal v Franklin).pdf",
  #                     "Doe v. Bolton Brief for Petitioners (Feminist).pdf",
  #                     "Doe v. Bolton Brief for Respondents.pdf",
  #                     "H.L. v Matheson. Brief for Appellant (feminist).docx",
  #                     "United States v Vuitch. Brief for Appellant %28United States%29.docx",
  #                     "United States v. Vuitch. Brief for Respondent (Feminist).pdf"))) %>% 
  rbind(litigant_txt)
```

@@

```{r}
box_write(litigant_all,
          file_name = "raw-litigant-brief-text.csv",
          dir_id = '162588272045')
```

### 2022-05-10 data-cleaning/01-shorten-amicus-text.Rmd
add missing amicus + lit briefs

# data
# data/processed amicus files/raw-amicus-brief-text.csv
amicus <- box_read("863216279471")
# data/processed amicus files/amicus summary.xlsx
alternate_rmv <- box_read("864995408351", sheet = "data") %>% 
  select(case, brief, id, alternative) %>% 
  filter(!is.na(alternative))
#data/processed amicus files/footnotes-confirmed.csv
footnotes_ids <- box_read("908607927934")
```

@@

```{r}
amicus <- amicus %>%
  mutate(footnotes_cor = str_count(txt_short, "footnotes counsel of record"),
         footnotes_1 = str_count(txt_short, "footnotes 1"))

@@

```{r}
table(amicus$footnotes_1)
```

@@

```{r}
amicus <- amicus %>% mutate(
         txt_short = case_when(
           grepl("footnotes counsel of record", txt_short)
           & (id %in% footnotes_ids$id) ~ 
             gsub(pattern = "footnotes counsel of record.*", replacement = "", x = txt_short),
           grepl("footnotes 1", txt_short)
           & (id %in% footnotes_ids$id | id == '861814132010') ~ 
             gsub(pattern = "footnotes 1.*", replacement = "", x = txt_short),
           T ~ txt_short),
         txt_short = str_squish(txt_short))
```

@@

```{r}
a <- amicus %>%
  mutate(footnotes_cor = str_count(txt_short, "footnotes counsel of record"),
         footnotes_1 = str_count(txt_short, "footnotes 1"))

table(a$footnotes_1)
```

```{r}
table(a$footnotes_cor)
```

@@

```{r}
# amicus <- amicus %>% select(case, brief, id, txt_short)
# 
# box_write(amicus,
#           file_name = "shortened-amicus-brief-text.csv",
#           dir_id = 145990409196)
```

>>>>

# data
# data/processed amicus files/raw-amicus-brief-text.csv
amicus <- box_read("863216279471")
# data/processed amicus files/amicus summary.xlsx
alternate_rmv <- box_read("864995408351", sheet = "data") %>% 
  select(case, brief, id, alternative) %>% 
  filter(!is.na(alternative))
#data/processed amicus files/footnotes-confirmed.csv
footnotes_ids <- box_read("908607927934") %>% rbind(861822172835)
```

@@

```{r}
amicus <- amicus %>%
  mutate(footnotes_cor = str_count(txt_short, "footnotes counsel of record"),
         footnotes_cor2 = str_count(txt_short, "footnotes \\* counsel of record"),
         footnotes_cor3 = str_count(txt_short, "footnotes \\* fn counsel of record"),
         footnotes_1 = str_count(txt_short, "footnotes 1"))

@@

```{r}
table(amicus$footnotes_cor2)
table(amicus$footnotes_cor3)
```

@@

```{r}
amicus <- amicus %>% mutate(
         txt_short = case_when(
           grepl("footnotes \\* counsel of record", txt_short) ~ 
             gsub(pattern = "footnotes \\* counsel of record.*", replacement = "", x = txt_short),
           grepl("footnotes counsel of record", txt_short) ~ 
             gsub(pattern = "footnotes counsel of record.*", replacement = "", x = txt_short),
           grepl("footnotes fn \\* counsel of record", txt_short) ~ 
             gsub(pattern = "footnotes fn \\* counsel of record.*", replacement = "", x = txt_short),
           grepl("footnotes 1", txt_short)  ~ 
             gsub(pattern = "footnotes 1.*", replacement = "", x = txt_short),
           T ~ txt_short),
         txt_short = str_squish(txt_short))
```

@@

```{r}
a <- amicus %>%
  mutate(footnotes_cor = str_count(txt_short, "footnotes \\* counsel of record"),
         footnotes_fn_cor = str_count(txt_short, "footnotes fn \\* counsel of record"),
         footnotes_1 = str_count(txt_short, "footnotes 1"))

table(a$footnotes_1)
table(a$footnotes_cor)
table(a$footnotes_fn_cor)
```

@@

```{r}
 amicus <- amicus %>% select(case, brief, id, txt_short)
# 
 box_write(amicus,
           file_name = "shortened-amicus-brief-text.csv",
           dir_id = 145990409196)
```

### 2022-05-10 data-cleaning/05-add-amicus-measures.Rmd
add missing amicus + lit briefs

# data/processed amicus files/amicus_clean_512_no_stride.csv
amicus_party <- box_read("942789542605") %>% select(id, brief_party) %>% distinct(id, brief_party)

# data/processed_amicus_files/shortened_amicus_brief_text.csv
amicus <- box_read("910635411098")

# data/processed amicus files/walkover_brief_names.csv
walkover <- box_read("941154488137")
```

@@

# change june v russo to case id = 999999
brief_info <- brief_info %>%
  mutate(Case = ifelse(is.na(Case), "999999", Case))

@@

```{r}
walkover$case_code <-  as.character(walkover$case_code)
walk_measures <- walkover %>%
  left_join(brief_info, by = c("case_code" = "Case", "brief_code" = "amicus_id"))

@@

```{r}
amicus <- amicus %>% left_join(., amicus_party, by = "id")
```

>>>>

# data/processed amicus files/amicus_clean_512_no_stride.csv
amicus_party <- box_read("942789542605") %>% select(id, brief_party) %>% distinct(id, brief_party) %>% 
  mutate(id = as.character(id))

# data/processed_amicus_files/shortened_amicus_brief_text.csv
amicus <- box_read("910635411098") %>% mutate(id = as.character(id))

# data/processed amicus files/walkover_brief_names.csv
walkover <- box_read("941154488137") %>% mutate(new_id = as.character(new_id))
```

@@

# change june v russo to case id = 999999
brief_info <- brief_info %>%
  mutate(Case = ifelse(is.na(Case), "999999", Case)) %>% 
  mutate(`Amicus Brief` = ifelse(`Amicus Brief` == "Stenberg v Carhart. Amics Brief for Petitioner by Agudath Israel of America.docx",
                                 "Stenberg v Carhart. Amicus Brief for Petitioner by Agudath Israel of America.docx",
                                 `Amicus Brief`))

@@

```{r}
walkover$case_code <-  as.character(walkover$case_code)
walk_measures <- walkover %>%
  left_join(brief_info, by = c("case_code" = "Case", "brief_code" = "amicus_id")) %>% 
  mutate(new_id = ifelse(old_id == "592236091833", "861822172835", new_id),
         name_correct = ifelse(old_id == "592236091833", "Stenberg v Carhart. Amicus Brief for Petitioner by Agudath Israel of America.docx", name_correct))

@@

```{r}
amicus <- amicus %>% left_join(., amicus_party, by = "id") %>% 
  mutate(brief_party = ifelse(id == "861822172835", 0, brief_party))
```
